DraftFunctions

### 2021-05-11 R/DraftFunctions.Rmd
Debugging zzz, other package import

# TrunkHeight formule : TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))
# CrownDiameter formule : CrownDiameter = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight
# RottenModel

pars <- list(MinDBHValue = 10, #in cm
  MaxAreaSlope = 27, #in %
  MaxTrailCenterlineSlope = 22, #in %
  MaxTrailCrossSlope = 4, #in %
  GrappleMaxslope = 20, #in %
  TreeMaxSlope = 22, #in %
  PlateauMaxSlope = 5, #in %
  SlopeDistance = 6, #in m (3m for each side)
  WaterSourcesBufferZone = 30, #in m
  MainTrailWidth = 5-6, #in m
  "2ndTrailWidth" = 4, #in m
  BigTrees = 50, #in cm
  ObjectiveBonus = 20-30, #in % (ObjectiveBonus >= 20 && ObjectiveBonus =< 30 ou c(20:30))
  CableLength = 40, #in m
  GrappleLength = 6, #in m
  IsolateTreeMinDistance = 100, #in m
  FutureTreesMinDiameter = 35, #in cm
  TreefallSuccessProportion = 0.6,
  TreefallOrientation = 30-45, #in degree (◦)
  TreeHollowPartForFuel = 1/3, #(Hollow) Part taken from hollow trees for fuel exploitation
  Purge = 0.14, # in m^3 of fuelwood/m^3 of logged trees  
  MaxTrailDensity = 200, #in m/ha
  MaxLandingArea = 1500, #in square meters
  TrunkHeightAllometry = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2)),
CrownDiameterAllometry = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight,
RottenModel = ) 
```

@@

  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>%  #remove obsolete columns
  mutate(CrownDiameter = exp((
  (ln(DBH)-alpha-error)/beta)
  )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))

@@

unique(Paracou6_2016_crown[(Paracou6_2016_crown$Taxo == "mean"),]$ScientificName) #which species are no recognized
length(unique(Paracou6_2016_crown$ScientificName)) #How many species are in the plot
```

@@

  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) #remove obsolete columns
  # mutate(CrownDiameter = exp((
  # (ln(DBH)-alpha-error)/beta)
  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))

>>>>

# TrunkHeight formule : TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))
# CrownDiameter formule : CrownDiameter = exp(((log(DBH)-alpha-error)/beta))/TreeHeight
# RottenModel

pars <- list(MinDBHValue = 10, #in cm
  MaxAreaSlope = 27, #in %
  MaxTrailCenterlineSlope = 22, #in %
  MaxTrailCrossSlope = 4, #in %
  GrappleMaxslope = 20, #in %
  TreeMaxSlope = 22, #in %
  PlateauMaxSlope = 5, #in %
  SlopeDistance = 6, #in m (3m for each side)
  WaterSourcesBufferZone = 30, #in m
  MainTrailWidth = 5-6, #in m
  "2ndTrailWidth" = 4, #in m
  BigTrees = 50, #in cm
  ObjectiveBonus = 20-30, #in % (ObjectiveBonus >= 20 && ObjectiveBonus =< 30 ou c(20:30))
  CableLength = 40, #in m
  GrappleLength = 6, #in m
  IsolateTreeMinDistance = 100, #in m
  FutureTreesMinDiameter = 35, #in cm
  TreefallSuccessProportion = 0.6,
  TreefallOrientation = 30-45, #in degree (◦)
  TreeHollowPartForFuel = 1/3, #(Hollow) Part taken from hollow trees for fuel exploitation
  Purge = 0.14, # in m^3 of fuelwood/m^3 of logged trees  
  MaxTrailDensity = 200, #in m/ha
  MaxLandingArea = 1500, #in square meters
  TrunkHeightAllometry = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2)),
CrownDiameterAllometry = exp(((log(DBH)-alpha-error)/beta))/TreeHeight,
RottenModel = ) 
```

@@

  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>%  #remove obsolete columns
  mutate(CrownDiameter = exp((
  (log(DBH)-alpha-error)/beta)
  )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))

@@

unique(Paracou6_2016_crown[(Paracou6_2016_crown$Taxo == "mean"),]$ScientificName) #which species are no recognized
length(unique(Paracou6_2016_crown$ScientificName)) #How many species are in the plot
```
#' @examples
#' data(Paracou6_2016)
#' if (!("DBH" %in% names(inventory))) {add_column(inventory, DBH = NA) #if DBH doesn't exist create it
#' inventory$DBH = inventory$CircCorr/pi} # and compute it
#' cleaninventory(inventory = Paracou6_2016)

@@

  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) #remove obsolete columns
  # mutate(CrownDiameter = exp((
  # (log(DBH)-alpha-error)/beta)
  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries)) # Mettre finalement l'objet créé dans le zzz.R
